% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{5}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}



\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{stmaryrd}
% Numbering is tied to sections (e.g., Proposition 2.1, 2.2, etc.)
% Theorems and Propositions (italic)
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
% Definitions and Corollaries (upright)
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{example}{Example}
% \newtheorem{algorithm}[theorem]{Algorithm}
% Optional: formatting for the proof environment
\renewenvironment{proof}
   {\par\noindent\textbf{Proof.}\ }
   {\hfill$\blacksquare$\par}


\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Estimating the risk of labour exploitation and abuse among transnational domestic workers in the UK},
  pdfauthor={Caroline Emberson; Scott Moser},
  colorlinks=true,
  linkcolor={black},
  filecolor={Maroon},
  citecolor={RoyalBlue},
  urlcolor={BrickRed},
  pdfcreator={LaTeX via pandoc}}


\title{Estimating the risk of labour exploitation and abuse among
transnational domestic workers in the UK}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Modern Slavery Among Domestic Workers: Comprehensive RDS
Analysis}
\author{Caroline Emberson \and Scott Moser}
\date{18, August 2025}
\begin{document}
\maketitle

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

\newpage

\section{Introduction}\label{introduction}

Labour exploitation has been defined as `work situations that deviate
significantly from standard working conditions as defined by legislation
or other binding legal regulations, concerning in particular
remuneration, working hours, leave entitlements, health and safety
standards and decent treatment'
((\citeproc{ref-european_union_for_fundamental_rights_2015}{\textbf{european\_union\_for\_fundamental\_rights\_2015?}}),
p.~10). In the operations and supply chain management literature,
businesses' respect for these kinds of employee labour rights began with
studies focused upon labour rights transgressions related to risk
reduction and risk communication and considered how to improve
employees' health and safety (Chinander
(\citeproc{ref-chinander_aligning_2001}{2001}); Wolf
(\citeproc{ref-wolf_operationalizing_2001}{2001})). Recently, more
serious labour rights abuses have come to the fore with studies
examining the challenges of severe labour abuse under the umbrella term
`modern slavery' (Gold et al. (\citeproc{ref-gold_modern_2015}{2015});
New (\citeproc{ref-new_modern_2015}{2015}); Benstead et al.
(\citeproc{ref-benstead_horizontal_2018}{2018}); Stevenson \& Cole
(\citeproc{ref-stevenson_modern_2018}{2018})). While this literature
offers important insights into these severe forms of labour exploitation
in global supply chains, the wider social sustainability literature has
been criticised for taking a de-humanised approach to the understanding
of workers and their working conditions (Soundararajan et al.
(\citeproc{ref-soundararajan_humanizing_2021}{2021})). Perhaps as a
result, little attention has been paid to workers' experiences of severe
forms of labour exploitation in the literature to date. While recent
projects seek to examine the phenomenon of worker voice in factory
settings (Trust (\citeproc{ref-leverhulme_trust_research_2022}{2022})),
nowhere are the realities of individual workers' experiences of employer
exploitation brought into sharper relief than in the setting of domestic
work in private households.

The authors of the Global Slavery Index estimate that there are
seventy-six million people employed in domestic work worldwide
((\citeproc{ref-ilo_walk_free_iom_2022}{\textbf{ilo\_walk\_free\_iom\_2022?}})).
According to Bonnet et al. (\citeproc{ref-bonnet_domestic_2022}{2022}),
eighty percent of this domestic work is unregulated and informal. Labour
exploitation has been identified as an extensive global problem within
the sector, with domestic work identified as one of five private sector
groupings which contribute the most to forced labour. Defined in the ILO
Forced Labour Convention, 1930 No.29, forced or compulsory labour is
`all work or service which is exacted from a person under the threat of
a penalty and for which the person has not offered himself or herself
voluntarily' (O (\citeproc{ref-ilo_what_2024}{2024})). Seventy-six
percent of domestic workers are women, and these workers represent four
percent of the total female workforce
((\citeproc{ref-ilo_walk_free_iom_2022}{\textbf{ilo\_walk\_free\_iom\_2022?}})).
Indeed, women in forced labour are much more likely to be in domestic
work than in any other occupation (ibid). The ILO suggest that female
domestic workers may be coerced through non-payment of wages; abuse of
vulnerability; subjected to physical and sexual violence or experience
threats against their family members. Such severe forms of labour
exploitation may be present alongside other, perhaps less severe but
equally illegal, practices which constitute various forms of labour
abuse. The criminalisation of both labour exploitation and abuse in a
domestic setting has developed in recent times, with legislation enacted
in the United Kingdom (UK), Europe, Australia and Norway to criminalise
such severe exploitation under the term `modern slavery'. However, even
where modern slavery laws are in place, reliance on traditional,
inspection-led, approaches to detection designed primarily to ensure
labour rights compliance within communal workplaces such as factories
mean that the number of reported cases of labour exploitation in private
dwellings may well severely underestimate actual exploitation levels.
This article aims to contribute to a more nuanced understanding of how
survey techniques may be developed to improve understanding of the
realities of workers' conditions by demonstrating the use of a
statistically robust estimation of the nature and proportion of labour
exploitation and abuse among domestic workers in the UK. This setting
was chosen due to long-standing national legislation criminalising
modern slavery introduced to the UK in 2015. Despite, or perhaps because
of this legislation, in recent years the number of potential victims
entering the UK's National Referral Mechanism (NRM), a scheme which
provides government support for those suspected to be modern slavery
survivors, has continued to increase. Nineteen thousand, one hundred and
twenty-five potential victims were recorded in 2024: the highest annual
figure since the NRM began
((\citeproc{ref-home_office_2025}{\textbf{home\_office\_2025?}})). In
2024, for the first time the number of cases of potential modern slavery
among females handled by the charity Unseen, who run the UK's modern
slavery helpline, were more prevalent than those among men (Carter
(\citeproc{ref-carter_women_2025}{2025})). Despite these worrying
headline statistics, and the persistence of specific concerns about high
levels of exploitation among domestic workers in the grey literature
(Kalayaan (\citeproc{ref-kalayaan_new_2008}{2008}); Mantouvalou
(\citeproc{ref-mantouvalou_modern_2016}{2016});
(\citeproc{ref-lawrs_2023}{\textbf{lawrs\_2023?}})), to our knowledge
no-one has yet estimated the nature and extent of labour exploitation
and abuse that may exist among domestic workers in the UK.

In contrast to overseas factory workers in globally dispersed, product,
supply chains, many service workers engaged in domestic work have
migrated to work in the UK. These transnational workers enter on
restricted visas where their employment---and their right to remain in
the country---is tied to their continuing employment. It is now ten
years since the UK's Modern Slavery Act was enacted. During its passage
through parliament, those advocating for the rights of domestic workers
were successful in expanding the final category boundaries of the
legislation to include, in Section 53, the specific definition of
(overseas) domestic workers as modern slavery victims (Caruana et al.
(\citeproc{ref-caruana_boundaries_2025}{2025})). These transnational
migrants are at particular risk of exploitation due to regulatory visa
restrictions and intersecting structural issues related to their gender,
the relative isolation of domestic work and a lack of supportive social
networks. This can mean that they fall out of legal migratory status.
Due to the social stigma attached to such illegal working, transnational
workers remaining in the UK without the right to work may be considered
a hidden, hard-to-reach, population. Extracting a sample of domestic
workers which includes this group raises difficulties when trying to
employ the normal statistical sampling methods considered necessary for
robust prevalence estimation. Perhaps due to these sampling
difficulties, we know relatively little about the nature of labour
exploitation among this particularly at-risk group of workers.
Fortunately, there has been significant interest in the development of
alternative methods for prevalence estimation which include such
hard-to-reach groups, with many scholars advocating and developing the
use of respondent-driven sampling (RDS) techniques to support
statistically robust estimators.

In this paper, we make two specific contributions to the operations and
supply chain management literature. First, we demonstrate the use of RDS
coupled with Network Scale-up Methods (N-SUM) to reach and sample
respondents' views of their working conditions among these,
predominantly female, transnational migrant domestic workers. We use the
data we obtain from these respondents to show how such a survey can be
used to estimate the proportion of workers experiencing labour
exploitation. Second, we begin to capture the nature and extent of
modern slavery as voiced by domestic service workers thereby, we
believe, expanding the nascent literature on worker voice which has, in
the main, focussed primarily upon factory workers (Stephens et al.
(\citeproc{ref-stephens_theorising_2024}{2024})). These contributions
not only extend our understanding of the risks of labour exploitation
and abuse among service workers engaged in domestic settings but also
show how it is possible to shed light on the severity of the
individuals' experience of exploitation through the construction of a
novel risk index. The remainder of this paper is structured as follows.
First, we describe our conceptual framework and introduce the context of
our study in more detail, highlighting what is already known about the
current population of domestic workers in the UK and the conditions in
which they work. Next, we describe our research methods. We review the
development of the respondent-driven sampling (RDS) techniques we used
and explain why this sampling method is suitable for our study. We then
describe our survey methods, including how we designed our survey
instrument, contacted our sample seeds and analysed our data. We then
present and discuss our findings, detailing the proportional estimate
that we calculated and the risk index we constructed. In our discussion,
we expand upon the implications of our findings for government policy,
enforcement practices and further research, including how these methods
may be used in future studies of labour exploitation in other sectoral
and geographic contexts. The limitations of our study are outlined,
before, finally, we conclude our article.

\section{Conceptualising Labour Exploitation and the Degree of
Risk}\label{conceptualising-labour-exploitation-and-the-degree-of-risk}

Modern slavery has been criticised by some for its overly extensive
scope: encapsulating a broad range of divergent sub-categories of
exploitation
((\citeproc{ref-oconnell_davidson_2015}{\textbf{oconnell\_davidson\_2015?}});
(\citeproc{ref-gutierrez-huerter_2023}{\textbf{gutierrez-huerter\_2023?}})).
For this reason, we used the International Labour Organization's
((\citeproc{ref-ilo_2012}{\textbf{ilo\_2012?}})) `Indicators of Forced
Labour' to identify the potential for severe labour exploitation and as
a basis for the quantification of our labour exploitation and abuse risk
index. The ILO identify eleven indicators designed to help understand
how forced labour arises and how it affects victims. These indicators
include: abuse of vulnerability; deception; restriction of movement;
isolation; physical and sexual violence; intimidation and threats;
retention of identity documents; withholding of wages; debt bondage;
abusive working and living conditions and excessive overtime. According
to the ILO, the presence of a single indicator in any given situation
may in some cases imply the existence of forced labour. However, it also
suggests that in other cases it may be necessary to look for several
indications which, taken together, may point to a case of forced labour.
We seek to refine this statement through the construction of a composite
index by which means a degree of risk related to the likelihood of a
domestic worker experiencing this most severe form of exploitation may
be distinguished from the likely occurrence of less severe, though
similarly illegal, forms of labour abuse.

\subsection{Evaluating the Degree of
Risk}\label{evaluating-the-degree-of-risk}

The study of risk management has a long tradition in operations and
supply chain management. Initially, the risks under consideration were
primarily related to ensuring continuity of the supply of goods and
services (see for example, Jüttner et al.
(\citeproc{ref-juttner_supply_2003}{2003})). Beginning with Anderson
(\citeproc{ref-anderson_critical_2006}{2006}) and Anderson \& Anderson
(\citeproc{ref-anderson_sustainability_2009}{2009}), however, a
literature stream of sustainability-related supply chain risk management
developed related specifically to the risks associated with the
environment and social justice. A normative consensus related to the
main stages of supply chain risk management has developed in the
literature, with a five-stage sequential model typically presented.
There have also been empirical studies of risk management within various
industrial supply chains in the United States and India (Tarei et al.
(\citeproc{ref-tarei_hybrid_2018}{2018}); Dellana et al.
(\citeproc{ref-dellana_scale_2021}{2021})), including the quantification
of a risk index for the petroleum supply chain (Tarei et al.
(\citeproc{ref-tarei_hybrid_2018}{2018})). Yet, while these authors
recognize the need for responsible management and its effect on societal
values, in line with other literature in the field they view risk from
the perspective of the corporate supply chain rather than examining the
risk of harm to the worker.

In our study, we conceptualise the risk of labour exploitation from the
workers' perspective. We conceive severe forms of labour exploitation
such as forced labour as one end of a spectrum ranging from illegal
employment practices that constitute labour abuse, such as wage payments
below legal minimum wage levels and health and safety violations,
through to the likelihood of criminal exploitation recognized in the UK
as modern slavery. Our assessment of this personal risk permits a degree
of risk to be assigned to various clusters of forced labour indicators
with the more indicators present, the stronger the likelihood that the
working conditions may be considered exploitative. Our approach,
therefore, includes, but goes beyond, assessing the likelihood of forced
labour by simply quantifying the proportion of survivors entering the
UK's National Referral Mechanism (NRM): a government system for survivor
support set up to identify whether there are positive grounds for the
identification of Modern Slavery. In our method, an NRM referral is used
as the strongest indicator of modern slavery risk, with lesser risks
assessed according to the degree to which cumulative indicators of
forced labour are reported.

\section{Case Setting: Labour Exploitation Risk Among Transnational
Migrant Domestic Workers In The
UK}\label{case-setting-labour-exploitation-risk-among-transnational-migrant-domestic-workers-in-the-uk}

Domestic work forms part of a broader industrial category of Personal
and Household Service work (PHS). Work in this category includes those
employed in `social work activities without accommodation' and
`activities of households as employers of domestic personnel'
((\citeproc{ref-european_commission_2012}{\textbf{european\_commission\_2012?}})).
In 2017, an estimated 980,000 people were engaged in PHS work in the UK
(Manoudi et al. (\citeproc{ref-manoudi_analysis_2018}{2018})). Manoudi
et al. (\citeproc{ref-manoudi_analysis_2018}{2018}) highlight that the
PHS sector is dominated by women and migrants, with many undeclared
foreign workers. Detailed statistics related to the country of origin of
domestic workers migrating to work in PHS in the UK are difficult to
isolate before 2019. Since that time, annual migration has fluctuated --
falling sharply in 2021 due in part to the COVID-19 pandemic, before
later rising again above pre-pandemic levels. In the year to December
2022, the UK Home Office reported that it had issued 18,533 Overseas
Domestic Worker visas
((\citeproc{ref-home_office_2023}{\textbf{home\_office\_2023?}})). These
domestic workers came from various countries in South America and Asia,
including many from the Philippines.

In 2023, Strauss \& Cocco (\citeproc{ref-strauss_britain_2023}{2023})
reported a big shift in the source countries of migrants arriving in the
UK on the Overseas Domestic Worker and other types of worker visas.
Transnational domestic workers from the Philippines and India accounted
for the single largest number of applications granted (10,186 and 3,858
visas respectively), followed by smaller, but still significant, numbers
of workers arriving from Bangladesh (465), Nigeria (446), Sri Lanka
(444), Egypt (422), and Ethiopia (285). In the same period, smaller
numbers of visa applications to work as a domestic worker in the UK were
also accepted from workers from other source countries including, but
not limited to, the Sudan, Nepal, Ghana, Kenya, Lebanon, Eritrea, Iran,
Turkey, Yemen, Malaysia, Thailand, and Morocco. This post-Brexit
increase in the diversity of source countries from which transnational
workers are drawn makes a more detailed analysis of the risk of labour
exploitation in the sector both timely and more urgent.

There is a long history of reports of exploitation in the domestic work
sector in the UK. In 2008, the civil society organisation Kalayaan,
which was formed to campaign for the formal recognition of migrant
domestic workers' rights in the UK, reported on the impact of proposed
changes to the UK immigration system on migrant domestic workers
(Kalayaan (\citeproc{ref-kalayaan_new_2008}{2008})). Their report
highlights government recognition of documented and unacceptable levels
of abuse and exploitation among domestic workers in the UK as early as
1996. At this stage, new policies, including the development of a
specialised visa allowing domestic workers to change employer during
their stay were introduced. However, in 2012, these visa conditions were
modified, tying domestic workers to a single employer and restricting
the length of time that they are permitted to remain in the country to a
period of six months (Gower (\citeproc{ref-gower_calls_2016}{2016})).
Overseas domestic worker visa holders are now, again, permitted to
change employers, but not to apply to renew their six-month long visa
unless they receive a positive `Conclusive Grounds' decision related to
exploitation considered to be modern slavery through the UK's National
Referral Mechanism (NRM) (Romero \& Fisher
(\citeproc{ref-romero_blueprint_2025}{2025})).

These reports highlight the underlying reasons for migrant domestic
workers' vulnerability, including workers' relative desperation for
work; their lack of social ties; unfamiliarity with English language and
culture; long working hours; lack of knowledge of their legal rights; a
lack of oversight of the private home as a workplace; their work forming
part of the informal economy; their reliance on their employer for
permission to work in the UK; and their lack of recourse to public
funds. As a result, migrant domestic workers are vulnerable to abuse
ranging from minor breaches of employment and health and safety law, to
physical and sexual violence, slavery, forced labour and trafficking.

That these conditions may persist is evidenced by a report from another
civil society organisation, the Latin American Women's Rights Service,
which describes the results from twelve in-depth interviews with Latin
American domestic workers in the UK. This report depicts high levels of
isolation, exploitation and abuse including a failure by employers to
provide written contracts or payslips; breaches of verbal agreements; a
requirement to perform different tasks from those indicated during
recruitment; increasing working hours with little or no time off;
excessive work days; a lack of paid holiday; many domestic workers not
registered with a GP; sexual harassment in the workplace; verbal or
physical abuse; employer surveillance; a lack of opportunity to change
working conditions; isolation and fear of seeking help; and high
reported levels of trafficking for labour exploitation
((\citeproc{ref-lawrs_2023}{\textbf{lawrs\_2023?}})).

Against this backdrop, we used respondent driven sampling (RDS) as a
sampling technique to recruit and survey domestic workers in the UK
about the working conditions they were experiencing to estimate the
nature and scale of abuse and exploitation based upon reports of their
conditions by domestic workers themselves.

\section{Research Methods}\label{research-methods}

{[}Scott- do feel free to edit as you see fit{]}

\subsection{Respondent-Driven Sampling (RDS) And Survey
Method}\label{respondent-driven-sampling-rds-and-survey-method}

Comprehensive descriptions and literature reviews of the development and
use of RDS to estimate the population size of a hidden population are
available elsewhere (Heckathorn
(\citeproc{ref-heckathorn_comment_2011}{2011}); Gile et al.
(\citeproc{ref-gile_methods_2018}{2018})). Suffice it to say, the
possibilities of the use of a one-wave snowball sampling to allow
researchers to obtain a sample of personal networks was posited by Frank
\& Snijders (\citeproc{ref-frank_estimating_1994}{1994}). Following the
identification of a set of original sample members known as seeds,
Heckathorn (\citeproc{ref-heckathorn_respondent-driven_1997}{1997});
Heckathorn (\citeproc{ref-heckathorn_respondent-driven_2002}{2002})
advocate the use of a double incentive to recompense participants not
only for their involvement, but also for their recruitment of further
participants in subsequent `waves' of participation by drawing upon the
social ties through which members of the hidden population are connected
to each other.

The typical number of original sample seeds is between two and ten:
chosen as heterogeneously as possible (Gile et al.
(\citeproc{ref-gile_methods_2018}{2018})). Though they may be subject to
both systematic and non-systematic errors, the use of snowballing
methods for the study of hidden populations, with the support of
monetary or symbolic rewards, has been advocated as a way of creating
robust recruitment embodying diversity in characteristics such as
ethnicity, gender and geographical location (Heckathorn
(\citeproc{ref-heckathorn_respondent-driven_1997}{1997}); Heckathorn
(\citeproc{ref-heckathorn_respondent-driven_2002}{2002})). In these
papers, Heckathorn advances the development of RDS to include
self-reported network size as a population estimator and bootstrapping
techniques to support the development of an estimator's confidence
intervals, an approach that has since been refined by others (Gile \&
Handcock (\citeproc{ref-gile_network_2015}{2015})). Such developments
derive a new class of indicators for the population mean and define a
corresponding bootstrap method to estimate the errors in RDS. The
resulting `network working model' permits the individual's connectedness
in the network to be tested, while reducing bias with respect to the
composition of the seeds. Snowball sampling is based upon the initial
recruitment of the original sample selection by means of convenience.
RDS also takes a non-random approach to seed selection, but relies upon
the social network structure that exists between participants to produce
a non-probabilistic sample (Goodman
(\citeproc{ref-goodman_comment_2011}{2011})). Incentive structure is
important---though this weakness is not a feature of our target hidden
population, some researchers have identified that younger men with
higher socio-economic status are less likely to participate (McCreesh et
al. (\citeproc{ref-mccreesh_respondent_2013}{2013})). Perhaps of more
concern, RDS has been described as a risky strategy since researchers
cannot be sure whether enough respondents have been recruited through
subsequent waves to eliminate bias within the original sample members
(Vincent \& Thompson (\citeproc{ref-vincent_estimating_2017}{2017})).

RDS has been widely used to sample a variety of hidden populations,
including HIV prevalence, rape and client-initiated gender-based
violence among sex workers (McCreesh et al.
(\citeproc{ref-mccreesh_evaluation_2012}{2012}); Schwitters et al.
(\citeproc{ref-schwitters_prevalence_2012}{2012})). While the RDS method
has proved limited when seeking to provide population heterogeneity by
geographical location (McCreesh et al.
(\citeproc{ref-mccreesh_evaluation_2011}{2011})), where these population
features are of lesser importance, such methods have been used
successfully. RDS methods have been used to survey other migrant
populations (Tyldum (\citeproc{ref-tyldum_surveying_2021}{2021})), while
such network-based referrals have been described as the only viable
method to reach many types of labour trafficking victims (Zhang
(\citeproc{ref-zhang_measuring_2012}{2012})) and have been used to
research exploitation among low-wage workers in three American cities
(Bernhardt et al. (\citeproc{ref-bernhardt_broken_2009}{2009})); a study
of labour trafficking in migrant communities in the city of San Diego
(Vincent \& Thompson (\citeproc{ref-vincent_estimating_2017}{2017}));
examination of the worst forms of child labour in the Indian state of
Bihar (Zhang et al. (\citeproc{ref-zhang_victims_2019}{2019})); and the
commercial sexual exploitation of children in Nepal (Jordan et al.
(\citeproc{ref-jordan_overcoming_2020}{2020})).

In the following section, we describe our methods, including how we
designed our survey, contacted our sample seeds, and analysed our data.
Our approach can best be described as Web-based RDS (Wejnert \&
Heckathorn (\citeproc{ref-wejnert_web-based_2008}{2008})). We designed a
web survey using the JISC online survey interface, suitable for our
respondents to complete via a mobile phone. Composite measures to
quantify the extent to which respondents were at risk of labour
exploitation, including severe forms of exploitation such as forced
labour, were constructed from existing exploitation typologies, notably
the ILO's Indicators ((\citeproc{ref-ilo_2012}{\textbf{ilo\_2012?}})).
The survey consisted of these 11 composite indicators and included
questions related to domestic workers' level of job satisfaction,
employment conditions, and demographic data such as nationality, age,
and gender. The main survey was conducted in the five months between
February and July 2023.

\subsection{Initial Sample Selection}\label{initial-sample-selection}

We selected our first wave of participants nonrandomly by convenience
sampling. Mobile phone numbers were used both to identify seed
participants and to act as a unique identifier for those whom they
referred. To avoid sample homophily, original sample members were
selected from three distinct domestic worker communities. This was
facilitated by civil society organisations who represented distinct
domestic worker communities. One was an exclusively online community of
transnational domestic workers working in the UK, the second represented
UK domestic workers of Filipino origin, and the third drew its
membership from the Latin American community of domestic workers, also
in the UK. Along with other academics with expertise in exploitation
within domestic work, representatives from these three organisations
also contributed to survey question design and facilitated the piloting
of an initial version of the survey (which was translated and made
available in four languages: English, Spanish, Tagalog, and Portuguese)
to selected domestic workers within each community.

\subsection{Survey Incentives: Incentive Design and Participation
Verification}\label{survey-incentives-incentive-design-and-participation-verification}

A double incentive scheme rewarded respondents both for completing the
questionnaire and for each referral who went on to engage with the
survey. The challenge of incentive design is to set the incentive at a
level that adequately rewards respondents' time and participation, but
that also avoids the risk of fraudulent participation due to too high a
monetary gain (Jordan et al.
(\citeproc{ref-jordan_overcoming_2020}{2020})). A sum of £10 was
provided for survey completion with a further £5 for each successful
nomination. While respondents were asked to nominate up to 10 domestic
workers within their existing social network, it was the first three of
these from whom participation was requested in subsequent waves. This
approach is akin to the use of vouchers in face-to-face studies as
advocated by Thompson (\citeproc{ref-thompson_new_2020}{2020}).

The ethical and practical issues related to the design and effective use
of incentives for RDS among vulnerable populations has been much
discussed in the literature; see, for example, Wang et al.
(\citeproc{ref-wang_respondent-driven_2005}{2005});
(\citeproc{ref-abdul-quader_2006}{\textbf{abdul-quader\_2006?}}); Singer
\& Bossarte (\citeproc{ref-singer_incentives_2006}{2006}); DeJong et al.
(\citeproc{ref-dejong_ethical_2009}{2009}); Semaan et al.
(\citeproc{ref-semaan_ethical_2009}{2009}); Brunovskis \& Surtees
(\citeproc{ref-brunovskis_untold_2010}{2010}); Semaan
(\citeproc{ref-semaan_time-space_2010}{2010}); Platt et al.
(\citeproc{ref-platt_adapting_2015}{2015}), including the specificities
of incentive use within web-based surveys (Cobanoglu \& Cobanoglu
(\citeproc{ref-cobanoglu_effect_2003}{2003})). Following the principles
of lottery use established by Brown et al.
(\citeproc{ref-brown_you_2006}{2006}) and Laguilles et al.
(\citeproc{ref-laguilles_can_2011}{2011}), we also designed our survey
to encourage the maximum extent of participation by entering all
respondents completing the questionnaire into a free prize draw for
£150. Research suggests that a high lottery provides the most
cost-effective incentive for obtaining complete responses (Gajic et al.
(\citeproc{ref-gajic_cost-effectiveness_2012}{2012})). While using
incentives to encourage participation would seem to be desirable, it is
worth noting the potential downside of respondents fabricating responses
to increase their remuneration (Robinson
(\citeproc{ref-robinson_sampling_2014}{2014})). To minimise this risk,
mobile phone numbers for each respondent and those whom they referred
were collated, and each of these numbers was called by one of the
authors of the paper to ascertain the veracity of the respondent as a
migrant domestic worker.

\section{Data Analysis}\label{data-analysis}

\subsection{Descriptive Statistics}\label{descriptive-statistics}

In total, we received completed online surveys from 97 respondents. Of
these respondents, 90 identified themselves as transnational migrants.
Forty-five percent regarded themselves as self-employed, 39\% identified
themselves as employees, and 16\% categorised their employment status as
that of a worker.

Of the 97 respondents, 64 (66\% of the total), and the largest single
nationality group, reported that they had a Filipina background. Other
nationalities represented included Dominican, Brazilian, Spanish,
Colombian, Bolivian, Venezuelan, Cuban, and Panamanian. Female domestic
workers made up 97\% of the sample, with 3\% of the sample comprised of
male domestic workers. The age structure of the domestic workers was
skewed towards those over 45 years old, with such workers representing
over half of the sample (see Table 1).

\subsection{Network Structure}\label{network-structure}

\section{Findings}\label{findings}

\subsection{Point Estimation and Confidence
Intervals}\label{point-estimation-and-confidence-intervals}

\subsection{Risk Index}\label{risk-index}

\section{Discussion}\label{discussion}

{[}Scott to add and revise{]}

\subsection{Implications for Policy}\label{implications-for-policy}

The UK Government has proved reluctant to respond to calls to remove the
restrictive, tied, visa conditions currently in force for those migrant
workers working in the UK on the Overseas Domestic Workers visa (Gower
(\citeproc{ref-gower_calls_2016}{2016})). Maintaining these restrictive
conditions prevents the ratification in the UK of C189, the
International Convention for Domestic Workers
((\citeproc{ref-ilo_2011}{\textbf{ilo\_2011?}})). If the estimates
resulting from our study are correct, these visa conditions place
migrant domestic workers at significant risk of serious forms of labour
exploitation including, in its most severe form, exploitation that
exhibits the characteristics of forced labour---legally considered a
form of modern slavery.

To reduce the vulnerability of transnational domestic workers to
this---and other---forms of labour exploitation, we urge policy-makers
to reconsider these discriminatory visa conditions and offer the same
freedoms to domestic workers that are enjoyed by other groups of workers
under UK law.

In addition, given the vulnerabilities experienced by workers due to the
private nature of the workplace, we would urge the UK government to
consider the regulation of domestic worker employers.

Finally, given the stigma and very real danger of deportation of those
migrant domestic workers who may have fallen out of legal migration
status, our evidence suggests that there is an urgent need for the UK
Government to enforce a firewall between immigration control and labour
exploitation if the true scale of abuse is to be made visible and the
perpetrators brought to justice.

\subsection{Implications for Practice}\label{implications-for-practice}

The UK Visa and Immigration service already offers rights-based training
to migrant domestic workers via UK embassies in certain source
countries. To reduce migrant domestic workers vulnerabilities, we
advocate the expansion of this training both to include explicit
training related to employment and labour rights within the UK and to
the rapidly expanding range of new source countries from where migrant
domestic workers are now drawn.

\subsection{Further Research}\label{further-research}

We believe that web-RDS combined with statistical estimators such as
NSUM offers an important method for the capture and comparison of
relative proportions of labour exploitation and abuse in sectors within
and beyond the UK. Network scale up methods, and potential enhancements
such as Generalised network scale up estimators offer to enhance
understanding, not least within operations and supply chain management
research, of the extent of labour exploitation in different sectors and
across industries.

\subsection{Limitations of the Study}\label{limitations-of-the-study}

As with any empirical research, our study is subject to limitations. In
terms of nationality, our sample is not representative of the
demographics of those domestic workers employed on Overseas Domestic
Worker Visas in 2022 the UK. Due to the increasing number of workers on
Overseas Domestic Work visas from the Indian sub-continent, attempts
were made also to seed respondents from this community. This proved
difficult, with anecdotal information suggesting that domestic workers
from this community rarely had access to a personal mobile phone. It is
not therefore possible to infer the nature and extent of labour
exploitation within this sub-section of the domestic worker population.

As the network structure of our sample demonstrates, even with a
well-designed incentive scheme it proved difficult to recruit
respondents from these communities of domestic workers in subsequent
sampling waves in the time available. Most of our respondents are
therefore original sample members draw from the three domestic worker
communities used to seed the survey.

\section{Conclusion}\label{conclusion}

\newpage

\subsection{Executive Summary}\label{executive-summary}

This analysis estimates the prevalence of modern slavery among domestic
workers in the UK using multiple RDS methodologies. We examine two
primary indicators across various population size assumptions and
estimation techniques.

\textbf{Key Findings:} - Below minimum wage prevalence (Q36): X.X\% -
Y.Y\% (95\% CI) - NRM referral experience (Q80): A.A\% - B.B\% (95\%
CI)\\
- Population size estimates: 980,000 - 1.74M domestic workers

\subsection{Sample Characteristics}\label{sample-characteristics}

\subsubsection{Recruitment Network
Structure}\label{recruitment-network-structure}

\begin{table}

\caption{\label{tbl-network}RDS Sample Network Characteristics}

\centering{

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{network\_stats }\OtherTok{\textless{}{-}} \FunctionTok{tibble}\NormalTok{(}
  \AttributeTok{Characteristic =} \FunctionTok{c}\NormalTok{(}\StringTok{"Total Sample Size"}\NormalTok{, }\StringTok{"Recruitment Waves"}\NormalTok{, }\StringTok{"Average Degree"}\NormalTok{, }
                    \StringTok{"Median Degree"}\NormalTok{, }\StringTok{"Seeds"}\NormalTok{, }\StringTok{"Longest Chain"}\NormalTok{, }\StringTok{"Mean Chain Length"}\NormalTok{),}
  \AttributeTok{Value =} \FunctionTok{c}\NormalTok{(}
    \FunctionTok{nrow}\NormalTok{(rd.dd),}
    \FunctionTok{max}\NormalTok{(rd.dd}\SpecialCharTok{$}\NormalTok{wave, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{),}
    \FunctionTok{round}\NormalTok{(}\FunctionTok{mean}\NormalTok{(rd.dd}\SpecialCharTok{$}\NormalTok{numRef, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{), }\DecValTok{1}\NormalTok{),}
    \FunctionTok{round}\NormalTok{(}\FunctionTok{median}\NormalTok{(rd.dd}\SpecialCharTok{$}\NormalTok{numRef, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{), }\DecValTok{1}\NormalTok{),}
    \FunctionTok{sum}\NormalTok{(rd.dd}\SpecialCharTok{$}\NormalTok{recruiter.id }\SpecialCharTok{==} \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{),}
    \StringTok{"TBD"}\NormalTok{, }\CommentTok{\# Calculate from recruitment chains}
    \StringTok{"TBD"}  \CommentTok{\# Calculate average chain length}
\NormalTok{  )}
\NormalTok{)}

\NormalTok{network\_stats }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gt}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{tab\_header}\NormalTok{(}\AttributeTok{title =} \StringTok{"Network Characteristics"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{fmt\_number}\NormalTok{(}\AttributeTok{columns =}\NormalTok{ Value, }\AttributeTok{decimals =} \DecValTok{1}\NormalTok{, }\AttributeTok{use\_seps =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

}

\end{table}%

\subsubsection{Demographic Composition}\label{demographic-composition}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create nationality breakdown}
\NormalTok{nationality\_summary }\OtherTok{\textless{}{-}}\NormalTok{ rd.dd }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(nationality\_cluster) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarise}\NormalTok{(}
    \AttributeTok{n =} \FunctionTok{n}\NormalTok{(),}
    \AttributeTok{percent =} \FunctionTok{round}\NormalTok{(}\FunctionTok{n}\NormalTok{() }\SpecialCharTok{/} \FunctionTok{nrow}\NormalTok{(rd.dd) }\SpecialCharTok{*} \DecValTok{100}\NormalTok{, }\DecValTok{1}\NormalTok{),}
    \AttributeTok{.groups =} \StringTok{\textquotesingle{}drop\textquotesingle{}}
\NormalTok{  )}

\FunctionTok{ggplot}\NormalTok{(nationality\_summary, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ nationality\_cluster, }\AttributeTok{y =}\NormalTok{ percent, }\AttributeTok{fill =}\NormalTok{ nationality\_cluster)) }\SpecialCharTok{+}
  \FunctionTok{geom\_col}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{geom\_text}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{label =} \FunctionTok{paste0}\NormalTok{(n, }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{("}\NormalTok{, percent, }\StringTok{"\%)"}\NormalTok{)), }\AttributeTok{vjust =} \SpecialCharTok{{-}}\FloatTok{0.5}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_viridis\_d}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Nationality Cluster"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Percentage"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Sample Distribution by Nationality"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\subsection{RDS Estimation Results}\label{rds-estimation-results}

\subsubsection{Model-Assisted Estimates by Population
Size}\label{model-assisted-estimates-by-population-size}

\begin{table}

\caption{\label{tbl-ma-estimates}Model-Assisted Estimates by Population
Size and Seed Selection}

\centering{

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Extract MA results and create comparison table}
\NormalTok{ma\_comparison }\OtherTok{\textless{}{-}} \FunctionTok{expand\_grid}\NormalTok{(}
  \AttributeTok{seed\_method =} \FunctionTok{c}\NormalTok{(}\StringTok{"sample"}\NormalTok{, }\StringTok{"random"}\NormalTok{, }\StringTok{"degree"}\NormalTok{),}
  \AttributeTok{pop\_size =} \FunctionTok{c}\NormalTok{(}\DecValTok{100000}\NormalTok{, }\DecValTok{953000}\NormalTok{, }\DecValTok{1000000}\NormalTok{, }\DecValTok{1500000}\NormalTok{),}
  \AttributeTok{indicator =} \FunctionTok{c}\NormalTok{(}\StringTok{"q36"}\NormalTok{, }\StringTok{"q80"}\NormalTok{, }\StringTok{"composite\_risk"}\NormalTok{)}
\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{rowwise}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{key =} \FunctionTok{paste0}\NormalTok{(seed\_method, }\StringTok{"\_"}\NormalTok{, pop\_size),}
    \AttributeTok{estimate =} \FunctionTok{ifelse}\NormalTok{(key }\SpecialCharTok{\%in\%} \FunctionTok{names}\NormalTok{(ma\_results),}
\NormalTok{                     ma\_results[[key]][[indicator]]}\SpecialCharTok{$}\NormalTok{estimate, }\ConstantTok{NA}\NormalTok{),}
    \AttributeTok{ci\_lower =} \FunctionTok{ifelse}\NormalTok{(key }\SpecialCharTok{\%in\%} \FunctionTok{names}\NormalTok{(ma\_results),}
\NormalTok{                     ma\_results[[key]][[indicator]]}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{1}\NormalTok{], }\ConstantTok{NA}\NormalTok{),}
    \AttributeTok{ci\_upper =} \FunctionTok{ifelse}\NormalTok{(key }\SpecialCharTok{\%in\%} \FunctionTok{names}\NormalTok{(ma\_results),}
\NormalTok{                     ma\_results[[key]][[indicator]]}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{2}\NormalTok{], }\ConstantTok{NA}\NormalTok{)}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ungroup}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(estimate))}

\CommentTok{\# Create formatted table}
\NormalTok{ma\_comparison }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{pop\_size\_f =}\NormalTok{ scales}\SpecialCharTok{::}\FunctionTok{comma}\NormalTok{(pop\_size),}
    \AttributeTok{estimate\_ci =} \FunctionTok{sprintf}\NormalTok{(}\StringTok{"\%.3f (\%.3f, \%.3f)"}\NormalTok{, estimate, ci\_lower, ci\_upper)}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(seed\_method, pop\_size\_f, indicator, estimate\_ci) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ indicator, }\AttributeTok{values\_from =}\NormalTok{ estimate\_ci) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gt}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{tab\_header}\NormalTok{(}\AttributeTok{title =} \StringTok{"Model{-}Assisted Estimates by Method"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{cols\_label}\NormalTok{(}
    \AttributeTok{seed\_method =} \StringTok{"Seed Selection"}\NormalTok{,}
    \AttributeTok{pop\_size\_f =} \StringTok{"Population Size"}\NormalTok{,}
    \AttributeTok{q36 =} \StringTok{"Below Min Wage"}\NormalTok{,}
    \AttributeTok{q80 =} \StringTok{"NRM Experience"}\NormalTok{, }
    \AttributeTok{composite\_risk =} \StringTok{"Composite Risk"}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{tab\_spanner}\NormalTok{(}\AttributeTok{label =} \StringTok{"Prevalence Estimates (95\% CI)"}\NormalTok{, }\AttributeTok{columns =} \FunctionTok{c}\NormalTok{(q36, q80, composite\_risk))}
\end{Highlighting}
\end{Shaded}

}

\end{table}%

\subsubsection{Traditional RDS Estimators
Comparison}\label{traditional-rds-estimators-comparison}

\begin{table}

\caption{\label{tbl-rds-comparison}RDS Estimator Comparison (N=980,000)}

\centering{

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Extract RDS estimates for standard population size}
\NormalTok{rds\_980k }\OtherTok{\textless{}{-}}\NormalTok{ rds\_results[[}\StringTok{"980000"}\NormalTok{]]}

\NormalTok{rds\_table }\OtherTok{\textless{}{-}} \FunctionTok{tibble}\NormalTok{(}
  \AttributeTok{Method =} \FunctionTok{c}\NormalTok{(}\StringTok{"RDS{-}I"}\NormalTok{, }\StringTok{"RDS{-}II"}\NormalTok{, }\StringTok{"Successive Sampling"}\NormalTok{),}
  \StringTok{\textasciigrave{}}\AttributeTok{Q36 Estimate}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{c}\NormalTok{(}
\NormalTok{    rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_i}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{estimate,}
\NormalTok{    rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_ii}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{estimate,}
\NormalTok{    rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_ss}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{estimate}
\NormalTok{  ),}
  \StringTok{\textasciigrave{}}\AttributeTok{Q36 95\% CI}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{c}\NormalTok{(}
    \FunctionTok{sprintf}\NormalTok{(}\StringTok{"(\%.3f, \%.3f)"}\NormalTok{, rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_i}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{1}\NormalTok{], rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_i}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{2}\NormalTok{]),}
    \FunctionTok{sprintf}\NormalTok{(}\StringTok{"(\%.3f, \%.3f)"}\NormalTok{, rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_ii}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{1}\NormalTok{], rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_ii}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{2}\NormalTok{]),}
    \FunctionTok{sprintf}\NormalTok{(}\StringTok{"(\%.3f, \%.3f)"}\NormalTok{, rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_ss}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{1}\NormalTok{], rds\_980k}\SpecialCharTok{$}\NormalTok{rds\_ss}\SpecialCharTok{$}\NormalTok{q36}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{2}\NormalTok{])}
\NormalTok{  ) }\CommentTok{\#...}
\end{Highlighting}
\end{Shaded}

}

\end{table}%

\newpage

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-anderson_critical_2006}
Anderson, D. R. (2006). The critical importance of sustainability risk
management. \emph{Risk Management (00355593)}, \emph{53}(4), 66--74.
\url{https://search.ebscohost.com/login.aspx?direct=true&db=buh&AN=20781527&site=ehost-live}

\bibitem[\citeproctext]{ref-anderson_sustainability_2009}
Anderson, D. R., \& Anderson, K. E. (2009). Sustainability risk
management. \emph{Risk Management and Insurance Review}, \emph{12}(1),
25--38. \url{https://doi.org/10.1111/j.1540-6296.2009.01152.x}

\bibitem[\citeproctext]{ref-benstead_horizontal_2018}
Benstead, A. V., Hendry, L. C., \& Stevenson, M. (2018). Horizontal
collaboration in response to modern slavery legislation: An action
research project. \emph{International Journal of Operations \&Amp;
Production Management}, \emph{38}(12), 2286--2312.
\url{https://doi.org/10.1108/IJOPM-10-2017-0611}

\bibitem[\citeproctext]{ref-bernhardt_broken_2009}
Bernhardt, A., Milkman, R. T., \& N. (2009). \emph{Broken laws,
unprotected workers: Violations of employment and labor laws in
america's cities} {[}\{UCLA\} \{IRLE\} Report.{]}.

\bibitem[\citeproctext]{ref-bonnet_domestic_2022}
Bonnet, F., Carre, F., \& Vanek, J. (2022). \emph{Domestic workers in
the world: A statistical profile. {WIEGO}}.
\url{https://www.wiego.org/research-library-publications/domestic-workers-world-statistical-profile/}

\bibitem[\citeproctext]{ref-brown_you_2006}
Brown, J. S., Schonfeld, T. L., \& Gordon, B. G. (2006). You may have
already won...'': An examination of the use of lottery payments in
research. \emph{{IRB}: Ethics \& Human Research}, \emph{28}(1), 12--16.

\bibitem[\citeproctext]{ref-brunovskis_untold_2010}
Brunovskis, A., \& Surtees, R. (2010). Untold stories: Biases and
selection effects in research with victims of trafficking for sexual
exploitation. \emph{International Migration}, \emph{48}(4), 1--37.

\bibitem[\citeproctext]{ref-carter_women_2025}
Carter, J. (2025, April 30). \emph{Women and girls at growing risk of
modern slavery, data reveals. Unseen}.
\url{https://www.unseenuk.org/latest-modern-slavery-helpline-data/}

\bibitem[\citeproctext]{ref-caruana_boundaries_2025}
Caruana, R., Crane, A., \& Ingram, C. (2025). The boundaries of modern
slavery: The role of exemplars in new category formation. \emph{Academy
of Management Journal}, \emph{68}(3), 507--539.
\url{https://doi.org/10.5465/amj.2022.0210}

\bibitem[\citeproctext]{ref-chinander_aligning_2001}
Chinander, K. R. (2001). Aligning accountability and awaress for
environmental performance in operations. \emph{Production and Operations
Management}, \emph{10}(3), 276--291.
\url{https://doi.org/10.1111/j.1937-5956.2001.tb00375.x}

\bibitem[\citeproctext]{ref-cobanoglu_effect_2003}
Cobanoglu, C., \& Cobanoglu, N. (2003). The effect of incentives in web
surveys: Application and ethical considerations. \emph{International
Journal of Market Research}, \emph{45}(4), 1--13.

\bibitem[\citeproctext]{ref-dejong_ethical_2009}
DeJong, J., Mahfoud, Z., Khoury, D., Barbir, F., \& Afifi, R. A. (2009).
Ethical considerations in {HIV}/{AIDS} biobehavioral surveys that use
respondent-driven sampling: Illustrations from lebanon. \emph{American
Journal of Public Health}, \emph{99}(9), 1562--1567.

\bibitem[\citeproctext]{ref-dellana_scale_2021}
Dellana, S., Rowe, W. J., \& Liao, Y. (2021). A scale for measuring
organizational risk management maturity in the supply chain.
\emph{Benchmarking: An International Journal}, \emph{29}(3), 905--930.
\url{https://doi.org/10.1108/BIJ-11-2020-0578}

\bibitem[\citeproctext]{ref-frank_estimating_1994}
Frank, O., \& Snijders, T. (1994). Estimating the size of hidden
populations using snowball sampling. \emph{Journal of Official
Statistics-Stockholm}, \emph{10}, 53--53.

\bibitem[\citeproctext]{ref-gajic_cost-effectiveness_2012}
Gajic, A., Cameron, D., \& Hurley, J. (2012). The cost-effectiveness of
cash versus lottery incentives for a web-based, stated-preference
community survey. \emph{The European Journal of Health Economics},
\emph{13}(6), 789--799.

\bibitem[\citeproctext]{ref-gile_methods_2018}
Gile, K. J., Beaudry, I. S., Handcock, M. S., \& Ott, M. Q. (2018).
Methods for inference from respondent-driven sampling data. \emph{Annual
Review of Statistics and Its Application}, \emph{5}, 65--93.
\url{https://doi.org/10.1146/annurev-statistics-031017-100704}

\bibitem[\citeproctext]{ref-gile_network_2015}
Gile, K. J., \& Handcock, M. S. (2015). Network model-assisted inference
from respondent-driven sampling data. \emph{Journal of the Royal
Statistical Society: Series A (Statistics in Society)}, \emph{178}(3),
619--639. \url{https://doi.org/10.1111/rssa.12091}

\bibitem[\citeproctext]{ref-gold_modern_2015}
Gold, S., Trautrims, A., \& Trodd, Z. (2015). Modern slavery challenges
to supply chain management. \emph{Supply Chain Management: An
International Journal}, \emph{20}(5), 485--494.
\url{https://doi.org/10.1108/SCM-02-2015-0046}

\bibitem[\citeproctext]{ref-goodman_comment_2011}
Goodman, L. A. (2011). Comment: On respondent-driven sampling and
snowball sampling in hard-to-reach populations and snowball sampling not
in hard-to-reach populations. \emph{Sociological Methodology},
\emph{41}(1), 347--353.

\bibitem[\citeproctext]{ref-gower_calls_2016}
Gower, M. (2016). \emph{Calls to change overseas domestic worker visa
conditions}.
\url{https://researchbriefings.files.parliament.uk/documents/SN04786/SN04786.pdf}

\bibitem[\citeproctext]{ref-heckathorn_respondent-driven_1997}
Heckathorn, D. D. (1997). Respondent-driven sampling: A new approach to
the study of hidden populations. \emph{Social Problems}, \emph{44}(2),
174--199. \url{https://doi.org/10.2307/3096941}

\bibitem[\citeproctext]{ref-heckathorn_respondent-driven_2002}
Heckathorn, D. D. (2002). Respondent-driven sampling {II}: deriving
valid population estimates from chain-referral samples of hidden
populations. \emph{Social problems}, \emph{49}(1), 11--34.

\bibitem[\citeproctext]{ref-heckathorn_comment_2011}
Heckathorn, D. D. (2011). Comment: Snowball versus respondent-driven
sampling. \emph{Sociological Methodology}, \emph{41}(1), 355--366.

\bibitem[\citeproctext]{ref-jordan_overcoming_2020}
Jordan, L., Chui, C. H. K., Larmar, S., \& O'Leary, P. (2020).
Overcoming methodological challenges in prevalence studies in developing
contexts with vulnerable children. \emph{International Social Work},
\emph{63}(3), 371--385.

\bibitem[\citeproctext]{ref-juttner_supply_2003}
Jüttner, U., Peck, H., \& Christopher, M. (2003). Supply chain risk
management: Outlining an agenda for future research. \emph{International
Journal of Logistics Research and Applications}, \emph{6}(4), 197--210.
\url{https://doi.org/10.1080/13675560310001627016}

\bibitem[\citeproctext]{ref-kalayaan_new_2008}
Kalayaan. (2008). \emph{The new bonded labour?}
\url{http://www.kalayaan.org.uk/documents/Kalayaan\%20Oxfam\%20report.pdf}

\bibitem[\citeproctext]{ref-laguilles_can_2011}
Laguilles, J. S., Williams, E. A., \& Saunders, D. B. (2011). Can
lottery incentives boost web survey response rates? Findings from four
experiments. \emph{Research in Higher Education}, \emph{52}(5),
537--553.

\bibitem[\citeproctext]{ref-manoudi_analysis_2018}
Manoudi, A., Weber, T., Scott, D., \& Hawley Woodall, J. (2018).
\emph{An analysis of personal and household services to support work
life balance for working parents and carers - google search}
{[}Synthesis Report \{ECE\} Thematic Review{]}. European Commission.
\url{https://www.google.com/search?q=An+analysis+of+Personal+and+Household+Services+to+support+work+life+balance+for+working+parents+and+carers&rlz=1C1GCEB_enGB932GB935&oq=An+analysis+of+Personal+and+Household+Services+to+support+work+life+balance+for+working+parents+and+carers&gs_lcrp=EgZjaHJvbWUyBggAEEUYOdIBCDIzNjNqMGo3qAIAsAIA&sourceid=chrome&ie=UTF-8}

\bibitem[\citeproctext]{ref-mantouvalou_modern_2016}
Mantouvalou, V. (2016). Modern slavery? The {UK} visa system and the
exploitation of migrant domestic workers. In \emph{British politics and
policy at {LSE}}.
\url{https://blogs.lse.ac.uk/politicsandpolicy/exploitation-of-migrant-domestic-workers-in-the-uk/.}

\bibitem[\citeproctext]{ref-mccreesh_respondent_2013}
McCreesh, N., Copas, A., Seeley, J., Johnston, L. G., Sonnenberg, P., \&
Hayes, R. J. (2013). Respondent driven sampling: Determinants of
recruitment and a method to improve point estimation. \emph{{PLoS}
{ONE}}, \emph{8}(10).

\bibitem[\citeproctext]{ref-mccreesh_evaluation_2012}
McCreesh, N., Frost, S. D. W., Seeley, J., Katongole, J., Tarsh, M. N.,
Ndunguse, R., Jichi, F., Lunel, N. L., Maher, D., Johnston, L. G.,
Sonnenberg, P., Copas, A. J., Hayes, R. J., \& White, R. G. (2012).
Evaluation of respondent-driven sampling. \emph{Epidemiology},
\emph{23}(1), 138--147. \url{https://www.jstor.org/stable/23214188}

\bibitem[\citeproctext]{ref-mccreesh_evaluation_2011}
McCreesh, N., Johnston, L. G., \& Copas, A. (2011). Evaluation of the
role of location and distance in recruitment in respondent-driven
sampling. \emph{International Journal of Health Geography},
\emph{10}(56).

\bibitem[\citeproctext]{ref-new_modern_2015}
New, S. J. (2015). Modern slavery and the supply chain: The limits of
corporate social responsibility? \emph{Supply Chain Management},
\emph{20}(6), 697--707. \url{https://doi.org/10.1108/SCM-06-2015-0201}

\bibitem[\citeproctext]{ref-ilo_what_2024}
O, I. L. (2024, January 28). \emph{What is forced labour?}
\url{https://www.ilo.org/topics/forced-labour-modern-slavery-and-trafficking-persons/what-forced-labour}

\bibitem[\citeproctext]{ref-platt_adapting_2015}
Platt, L., Luthra, R., \& Frere-Smith, T. (2015). Adapting chain
referral methods to sample new migrants: Possibilities and limitations.
\emph{Demographic Research}, \emph{33}, 665--700.

\bibitem[\citeproctext]{ref-robinson_sampling_2014}
Robinson, O. C. (2014). Sampling in interview-based qualitative
research: A theoretical and practical guide. \emph{Qualitative Research
in Psychology}, \emph{11}(1), 25--41.

\bibitem[\citeproctext]{ref-romero_blueprint_2025}
Romero, A., \& Fisher, O. (2025). \emph{Blueprint for safer and fairer
migration for low-paid work}. Focus on Labour Exploitation.
\url{https://labourexploitation.org/app/uploads/2025/06/Flex-Report-Blueprint-for-safer-and-fairer-migration-for-low-paid-work_final_30_June-.pdf}

\bibitem[\citeproctext]{ref-schwitters_prevalence_2012}
Schwitters, A., Swaminathan, M., \& Serwadda, D. (2012). Prevalence of
rape and client-initiated gender-based violence among female sex
workers: Kampala, uganda. \emph{{AIDS} Behaviour}, \emph{19}, 68--76.

\bibitem[\citeproctext]{ref-semaan_time-space_2010}
Semaan, S. (2010). Time-space sampling and respondent-driven sampling
with hard-to-reach populations. \emph{Methodological Innovations
Online}, \emph{5}(2), 60--75.

\bibitem[\citeproctext]{ref-semaan_ethical_2009}
Semaan, S., Santibanez, S., Garfein, R. S., Heckathorn, D. D., \&
Jarlais, D. C. (2009). Ethical and regulatory considerations in {HIV}
prevention studies employing respondent-driven sampling.
\emph{International Journal of Drug Policy}, \emph{20}(1), 14--27.

\bibitem[\citeproctext]{ref-singer_incentives_2006}
Singer, E., \& Bossarte, R. M. (2006). Incentives for survey
participation: When are they {``coercive''}? \emph{American Journal of
Preventive Medicine}, \emph{31}(5), 411--418.

\bibitem[\citeproctext]{ref-soundararajan_humanizing_2021}
Soundararajan, V., Wilhelm, M. M., \& Crane, A. (2021). Humanizing
research on working conditions in supply chains: Building a path to
decent work. \emph{Journal of Supply Chain Management}, \emph{57}(2),
3--13. \url{https://doi.org/10.1111/jscm.12260}

\bibitem[\citeproctext]{ref-stephens_theorising_2024}
Stephens, V., Benstead, A. V., Goworek, H., Charles, E., \& Lukic, D.
(2024). Theorising worker voice for supply chain justice --
communication, representation and recognition. \emph{International
Journal of Operations \&Amp; Production Management}, \emph{45}(3),
653--676. \url{https://doi.org/10.1108/IJOPM-06-2023-0528}

\bibitem[\citeproctext]{ref-stevenson_modern_2018}
Stevenson, M., \& Cole, R. (2018). Modern slavery in supply chains: A
secondary data analysis of detection, remediation and disclosure.
\emph{Supply Chain Management: An International Journal}, \emph{23}.
\url{https://doi.org/10.1108/SCM-11-2017-0382}

\bibitem[\citeproctext]{ref-strauss_britain_2023}
Strauss, D., \& Cocco, F. (2023). \emph{Britain after brexit: The
surprising surge in skilled migrants}.

\bibitem[\citeproctext]{ref-tarei_hybrid_2018}
Tarei, P. K., Thakkar, J. J., \& Nag, B. (2018). A hybrid approach for
quantifying supply chain risk and prioritizing the risk drivers: A case
of indian petroleum supply chain. \emph{Journal of Manufacturing
Technology Management}, \emph{29}(3), 533--569.
\url{https://doi.org/10.1108/JMTM-10-2017-0218}

\bibitem[\citeproctext]{ref-thompson_new_2020}
Thompson, S. (2020). \emph{New estimates for network sampling}.

\bibitem[\citeproctext]{ref-leverhulme_trust_research_2022}
Trust, L. (2022). \emph{Research project grants. Grant listings}.
\url{https://www.leverhulme.ac.uk/listings?field_grant_scheme_target_id=15}

\bibitem[\citeproctext]{ref-tyldum_surveying_2021}
Tyldum, G. (2021). Surveying migrant populations with respondent-driven
sampling. Experiences from surveys of east-west migration in europe.
\emph{International Journal of Social Research Methodology},
\emph{24}(3), 341--335.

\bibitem[\citeproctext]{ref-vincent_estimating_2017}
Vincent, K., \& Thompson, S. (2017). Estimating population size with
link-tracing sampling. \emph{Journal of the American Statistical
Association}, \emph{112}(519), 1286--1295.
\url{https://doi.org/10.1080/01621459.2016.1212712}

\bibitem[\citeproctext]{ref-wang_respondent-driven_2005}
Wang, J., Carlson, R. G., Falck, R. S., Siegal, H. A., Rahman, A., \&
Li, L. (2005). Respondent-driven sampling to recruit {MDMA} users: A
methodological assessment. \emph{Drug and Alcohol Dependence},
\emph{78}(2), 147--157.

\bibitem[\citeproctext]{ref-wejnert_web-based_2008}
Wejnert, C., \& Heckathorn, D. D. (2008). Web-based network sampling:
Efficiency and efficacy of respondent-driven sampling for online
research. \emph{Sociological Methods \& Research}, \emph{37}(1),
105--134.

\bibitem[\citeproctext]{ref-wolf_operationalizing_2001}
Wolf, F. G. (2001). Operationalizing and testing normal accident theory
in petrochemical plants and refineries. \emph{Production and Operations
Management}, \emph{10}(3), 292--305.
\url{https://doi.org/10.1111/j.1937-5956.2001.tb00376.x}

\bibitem[\citeproctext]{ref-zhang_measuring_2012}
Zhang, S. X. (2012). Measuring labour trafficking: A research note.
\emph{Crime, Law and Social Change}, \emph{58}, 469--482.

\bibitem[\citeproctext]{ref-zhang_victims_2019}
Zhang, S. X., Dank, M., Vincent, K., Narayanan, P., Bharadwaj, S., \&
Balasubramaniam, S. M. (2019). Victims without a voice: Measuring worst
forms of child labor in the indian state of bihar. \emph{Victims \&
Offenders}, \emph{14}(7), 832--858.

\end{CSLReferences}

\newpage

\appendix

\section{Appendix A}\label{appendix-a}




\end{document}
